Evaluation of performances

### 2021-09-02 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

```{r eval-performance-2, warning=FALSE}
table2 <- df_perf %>%
  group_by(learner_group) %>%
  slice(which.min(rmse_aggr)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(rmse_aggr) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se
  ) %>%
  select(-`Learner ID`, -rsq) %>%
  relocate(RMSE, .after = Filter) %>%
  relocate(`SE`, .after = RMSE) %>%
  select(-iter)

@@

results_aggr %>%
  ggplot(aes(x = rmse_aggr, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  ggbeeswarm2::geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 2.5) +
  # scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  # scale_color_viridis_d(breaks = sort(levels(results_aggr$learner_group))) +
  scale_color_viridis_d(breaks = results_aggr$learner_group) +

  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 40), breaks = seq(28, 40, 2)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse_aggr < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste0(filter, ",", round(rmse_aggr, 2))),
    size = 4,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr(base_size = 14) +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  # replace iter IDs by individual fold names
  dplyr::mutate(iter = as.character(iter)) %>% 
  dplyr::mutate(iter = case_when(learner.id == "XGBOOST MBO CMIM" & iter == 1 ~ "Luiando",
                                 learner.id == "XGBOOST MBO CMIM" & iter == 2 ~ "Laukiz1",
                                 learner.id == "XGBOOST MBO CMIM" & iter == 3 ~ "Oiartzun",
                                 learner.id == "XGBOOST MBO CMIM" & iter == 4 ~ "Laukiz2",

@@

                                 TRUE ~ as.character(iter))) %>% 
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::mutate(fw.perc = fw.perc * 100) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF \\\\ Relief" = "RF MBO Relief", "XGB \\\\ CMIM" = "XGBOOST MBO CMIM",
    "SVM \\\\ Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(`Test Plot` = as.character(`Test Plot`)) %>%
  dplyr::mutate("Features (\\#)" = case_when(
    # numbers here are the respective sums of the training sets (without the mentioned plot acting as the test set)
    `Test Plot` == "Laukiz1" ~ paste0(as.character(ceiling((`Features (\\%)` * 1249) / 100)), "/1249"),
    `Test Plot` == "Laukiz2" ~ paste0(as.character(ceiling((`Features (\\%)` * 1357) / 100)),"/1357"),
    `Test Plot` == "Luiando" ~ paste0(as.character(ceiling((`Features (\\%)` * 1507) / 100)),"/1507"),
    `Test Plot` == "Oiartzun" ~ paste0(as.character(ceiling((`Features (\\%)` * 1311) / 100)),"/1311"),
  )) %>%
  dplyr::group_by(Learner) %>%
  dplyr::arrange(Learner, `Test Plot`) %>% 
  dplyr::select(Learner, `Test Plot`, "Features (\\%)", "Features (\\#)")

>>>>

```{r eval-performance-2, warning=FALSE}
table2 <- df_perf %>%
  group_by(learner_group) %>%
  slice(which.min(rmse_aggr)) %>%
  mutate(filter = replace(filter, is.na(filter), "No Filter")) %>%
  arrange(rmse_aggr) %>%
  # remove Task info for featureless.learner
  dplyr::mutate(task.id = case_when(learner.id == "regr.featureless" ~ "-", TRUE ~ as.character(task.id))) %>%
  dplyr::rename(
    "Model" = learner_group,
    "Learner ID" = learner.id,
    "Task" = task.id,
    "Filter" = filter,
    "RMSE" = rmse_aggr,
    "SE" = se
  ) %>%
  select(-`Learner ID`, -rsq) %>%
  relocate(RMSE, .after = Filter) %>%
  relocate(`SE`, .after = RMSE) %>%
  select(-iter)

@@

results_aggr %>%
  ggplot(aes(x = rmse_aggr, y = task.id)) +
  # geom_jitter(aes(color = learner_group), size = 2, width = 0, height = 0.3) +
  # geom_dotplot(aes(fill = learner_group), binaxis="y",
  #                        stackdir="up") +
  ggbeeswarm2::geom_beeswarm(groupOnX = FALSE, aes(color = learner_group), size = 2.5) +
  # scale_color_nejm(breaks = sort(levels(results_aggr$learner_group))) +
  # scale_color_viridis_d(breaks = sort(levels(results_aggr$learner_group))) +
  scale_color_viridis_d(breaks = results_aggr$learner_group) +
  labs(x = "RMSE", y = "Task", color = "Learner") +
  guides(size = FALSE) +
  scale_x_continuous(limits = c(27, 40), breaks = seq(28, 40, 2)) +
  geom_label_repel(
    # subset data to remove out of bounds values
    data = results_aggr[results_aggr$rmse_aggr < 100, ],
    # from ggbeeswarm, avoid overlapping of points by labels
    position = position_quasirandom(),
    aes(label = paste0(filter, ",", round(rmse_aggr, 2))),
    size = 4,
    min.segment.length = 0.1,
    seed = 123,
    point.padding = 0.5
  ) +
  theme_pubr(base_size = 14) +
  theme(
    panel.grid.major.y = element_line(size = 0.1, linetype = "dashed"),
    axis.title.y = element_blank(),
    legend.text = element_text(size = 13),
    legend.title = element_text(size = 13),
    axis.text.y = element_text(angle = 45),
    plot.margin = unit(c(6, 6, 6, 0), "pt")
  )
```

@@

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  # replace iter IDs by individual fold names
  dplyr::mutate(iter = as.character(iter)) %>%
  dplyr::mutate(iter = case_when(
    learner.id == "XGBOOST MBO CMIM" & iter == 1 ~ "Luiando",
    learner.id == "XGBOOST MBO CMIM" & iter == 2 ~ "Laukiz1",
    learner.id == "XGBOOST MBO CMIM" & iter == 3 ~ "Oiartzun",
    learner.id == "XGBOOST MBO CMIM" & iter == 4 ~ "Laukiz2",

@@

    TRUE ~ as.character(iter)
  )) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::mutate(fw.perc = fw.perc * 100) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF \\\\ Relief" = "RF MBO Relief", "XGB \\\\ CMIM" = "XGBOOST MBO CMIM",
    "SVM \\\\ Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(`Test Plot` = as.character(`Test Plot`)) %>%
  dplyr::mutate("Features (\\#)" = case_when(
    # numbers here are the respective sums of the training sets (without the mentioned plot acting as the test set)
    `Test Plot` == "Laukiz1" ~ paste0(as.character(ceiling((`Features (\\%)` * 1249) / 100)), "/1249"),
    `Test Plot` == "Laukiz2" ~ paste0(as.character(ceiling((`Features (\\%)` * 1357) / 100)), "/1357"),
    `Test Plot` == "Luiando" ~ paste0(as.character(ceiling((`Features (\\%)` * 1507) / 100)), "/1507"),
    `Test Plot` == "Oiartzun" ~ paste0(as.character(ceiling((`Features (\\%)` * 1311) / 100)), "/1311"),
  )) %>%
  dplyr::group_by(Learner) %>%
  dplyr::arrange(Learner, `Test Plot`) %>%
  dplyr::select(Learner, `Test Plot`, "Features (\\%)", "Features (\\#)")
